Virtual Memory Assisted Transactional Memory for Dynamic Languages

### 2014-05-27 talk/dls2014/paper/paper.tex
talk a bit about jit-integration

@@

\subsection{Real-World Benchmarks}

>>>>

We evaluate our system in a Python interpreter called
PyPy\footnote{www.pypy.org}. PyPy is an implementation of an
interpreter for the Python language. It has a special focus on speed,
as it provides a just-in-time (JIT) compiler to speed up applications
running on top of it. For comparison, we also do evaluation on other
Python interpreters:
\begin{description}
\item[CPython] is the reference implementation of the Python
  language. It is the most widely used interpreter for this language.
  The implementation uses a GIL for synchronisation in multi-threaded
  execution and it does not feature a JIT compiler.
\item[Jython] is an implementation of Python on top of the Java Virtual
  Machine (JVM). Instead of a GIL, this interpreter uses fine-grained
  locking for synchronisation. This enables true parallelism when
  executing code on multiple threads. In addition, its integration
  with the JVM provides it with a JIT compiler for faster execution.
\end{description}

Here, we will not go into detail about the integration of our STM
system with PyPy's JIT. In fact, we will disable it for all benchmarks
except those in section \ref{sec:real-world-bench}. We would like to
regard it as a simple performance enhancement, but that is not what
happens in reality. First, since the JIT is a tracing
JIT\remi{explain?}  running in multiple threads, it may compile
different things in each run because of the non-deterministic
thread-scheduling of the operating system (OS). Second, it is able to
remove some allocations in some cases. Because compilation is already
non-deterministic, so is this allocation-removal. And third, we did
not have enough time to optimise integration with STM so that the JIT
exposes the overhead of STM more by speeding up all the rest.

Overall, we believe that disabling it on all benchmarks except the
real-world benchmarks in section \ref{sec:real-world-bench} is better
because we can minimise non-determinism. We also do not want to depend
on the capabilities of the JIT in these experiments.

% benchmarks with: pypy-c--Ojit-d1454093dd48+-14-05-26-17:16
% that's with stmgc 70c403598485

% Sometimes with JIT, sometimes without.
% For scaling & memory w/o jit, since the jit can optimize away
% many allocations and exposes the overhead more.

@@

\subsection{Real-World Benchmarks\label{sec:real-world-bench}}
